Books and Babies: An Analysis of the Relationship between Literacy Rate and Fertility Rate in South Asia (2000-2020)

### 2024-03-31 output/paper/paper.qmd
update paper.qmd

---
title: "Analyzing the Relationship between Female Fertility Rate and Female Literacy Rate in South Asia"
author: "Jagpreet Singh"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
date-format: long
bibliography: references.bib
execute: 
  echo: false
format: pdf
fig-pos: "H"
abstract: TBD
---

>>>>

---
title: "Books and Babies: An Analysis of the Relationship between Literacy Rate and Fertility Rate in South Asia (2000-2020)"
author: "Jagpreet Singh"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
date-format: long
bibliography: references.bib
execute: 
  echo: false
format: pdf
fig-pos: "H"
abstract: TBD
---
